The effects of linkage disequilibrium on maintaining balanced polymorphisms in seasonal adaptation

### 2019-12-13 writing/manuscript.Rmd
Small changes to the introduction

Genetic polymorphisms can provide a cache of diversity that contributes to adaptation in highly variable ecosystems [Gulisija2016]. Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014]. Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016]. Understanding the role of seasonality on adaptation can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].

@@

Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population. We study how the rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contribute to segregation lift. By including the metrics Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.

>>>>

Genetic polymorphisms can provide a cache of diversity that contributes to adaptation in highly variable ecosystems [Gulisija2016]. Fluctuating selection can maintain polymorphisms in seasonal environments if strong selective pressure towards both homozygous genotypes varies seasonally [@Novak2017, @Bergland2014]. Seasonality can drive powerful selection fluctuations, especially for organisms which have short a generation time of less than a month [@Messer2016]. Understanding the role of seasonality plays in maintaining genetic polymorphisms can allow more accurate predictions to be made about the capacity for organisms to adapt to climate change conditions [@Fournier-Level2016].

@@

Our model recreates and builds upon the work of @Wittman2017 to understand how linkage disequilibrium contributes to maintaining polymorphisms in a natural population. We study how the rate of crossover, epistasis, number of generation per season, population size, allelic dominance, and seasonal balance contribute to segregation lift. Climate change models predict a change in seasonal timing, with a lengthened and earlier summer and a milder shorter winter @[Bradshaw2006]. The seasonal balance metric allows our model to include effects of changing length of seasons to understand how a longer summer may influence segregation lift. Finally, we test how allelic interactions effect the dynamics of seasonal adaptation.
